%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Caden McArthur   } \\ \vspace{1pt}
    \small 918-521-7500 $|$ \href{mailto:x@x.com}{\underline{email: Caden.mcarthur@gmail.com}} $|$ 
    \underline{www.linkedin.com/in/cadenmcarthur/} $|$
    \underline{https://github.com/cmac2112}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bethel College}{North Newton, Ks}
      {Bachelor of Science in Computer Science, Minor in Mathematics}{}
      
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Software Developer | C\#, Javascript, Blazor, EfCore, SQL}{Dec 2024 --  Present}
      {INTRUST Bank}{Wichita, Ks}
      \resumeItemListStart
        \resumeItem{\textbf{Designed and developed internal banking applications} for managing investment wealth accounts, tracking escheated accounts, and logging physical security incidents with integrated image/video uploads. Continually updated internal development nuget library with new components and enhancements used across all apps.}
        \resumeItem{\textbf{Built automation tools and dashboards} including an employee badge tracker that syncs profile images across Microsoft products, and enhanced an app control platform with connection monitoring algorithms, GitHub issue tracking, and usage analytics for business unit visibility.  }
        \resumeItem{\textbf{Led the migration of bank development operations to Azure DevOps}, developing test applications and implementing automated CI/CD pipelines to streamline and accelerate cloud deployments and helping fellow developers familiarize themselves with Azure products. }
      \resumeItemListEnd
    \resumeSubheading
    {Front-End Software Engineer Intern | Typescript, React}{May 2024 -- Aug. 2024}
    {Leggett and Platt}{Lenexa, Ks}
    \resumeItemListStart
    \resumeItem{Developed \textbf{React} components for an internal home furniture application using \textbf{TypeScript} and \textbf{Tailwind CSS}, streamlining business operations by assisting in the transition away from spreadsheets. }
    \resumeItem{Implemented in-platform communication features, and \textbf{integrated multi-language support}, enabling accessibility for hundreds of employees across 20+ branches across North America, Europe, and Asia.}
    \resumeItem{\textbf{Participated in SCRUM Agile Methodology}, contributing to sprint planning, daily stand-ups, and retrospectives to ensure efficient collaboration and project delivery. Utilized \textbf{DevOps tools} for communication, version control, and deployment workflows }
    \resumeItemListEnd
    \resumeSubheading
      {Software Developer | Typescript/Javascript, React, Python, SQL }{Jan. 2024 -- Dec. 2024}
      {Bethel College}{North Newton, Ks}
      \resumeItemListStart
        \resumeItem{Coordinated with managers to build new independent, full stack careers site application to replace old legacy site using \textbf{React, Node, and MySQL}  }
        \resumeItem{Developed and deployed \textbf{Docker containers} for applications to ensure consistent development environments. }
        \resumeItem{Developed python scripts to automate collection of ACT, SAT, and ACCUPLACER test scores for the school.}
    \resumeItemListEnd

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Solar Eye} $|$ \emph{React, Three.Js/WEBGL, GLSL, }}{NASA Hackathon Winner}
          \resumeItemListStart
            \resumeItem{Built a solar system simulator using data from NASA API's to display orbits of near earth objects and teach users about keplarian orbital parameters and the dangers of near earth asteroids. \textbf{Received multiple NASA awards}}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Course Search} $|$ \emph{React, Node, MySQL}}
          {May 2024 -- August 2024}
          \resumeItemListStart
            \resumeItem{Developed a course search application for Bethel to allow students to better find buildings and rooms on campus using React. Accumulated over 1000 uses during fall 2024 semester.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{BCSocial} $|$ \emph{React, Node, MySQL, Docker,} Project Management, JIRA, CI/CD}{Aug 2024 -- Dec 2024}
          \resumeItemListStart
            \resumeItem{Built a social media app to allow student organizations to better communicate to students about events on campus. Managed project development using SCRUM and set user stories for each member every week through JIRA. Integrated CI/CD pipelines for automated testing, building, and deployment through Google Cloud Run and Github Actions}
          \resumeItemListEnd
          
\resumeItemListEnd
    \resumeSubHeadingListEnd
\section{Leadership}
\textbf{Bethel Software Society - Founder}
\resumeItemListStart
    \resumeItem{Established Bethel College's software club, providing mentorship to guide students toward successful post-graduation careers in the tech industry. Integrated CI/CD pipelines for projects, managed projects with SCRUM, and received multiple \textbf{awards for a project submitted to hackathons such as NASA's Space Apps Hackathon.} Voted "Most Promising New Student Organization" by faculty and staff of the college.}
\resumeItemListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, JavaScript/TypeScript, HTML/CSS,  SQL } \\
     \textbf{Developer Tools}{: Git, Docker,  CI/CD, Azure } \\
     \textbf{Libraries/Frameworks}{: React, Blazor}}\newline
    \textbf{Also Familar With}{: C,  Google Cloud Platform, Angular, Flask, Python, TensorFlow }}
 \end{itemize}


%-------------------------------------------
\end{document}
